VFTS682: a confirmed dynamical ejection?

### 2018-05-09 VFTS682.tex
./aa.cls

  \begin{tabular}[htbp]{l|c|c}
    Parameter & Value & Source\\ \hline\hline
    RA \hfill[degree] &  84.73 $\pm$  0.036 & \multirow{4}{*}{Gaia DR2}\\
    DE \hfill [degree] & -69.07 $\pm$  0.05  & \\
    $\mu_\mathrm{RA}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 1.84 $\pm$ 0.07 & \\
    $\mu_\mathrm{DE}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & 0.78 $\pm$ 0.08& \\
    $\delta v_\mathrm{rad}$  \hfill[$\kms$] & -45 $\pm$ 25 & \cite{bestenlehner:11}\\
    \hline
  \end{tabular}
  \label{tab:vfts682}
\end{table}

>>>>

  \begin{tabular}[htbp]{l|c|c}
    Parameter & Value & Source\\ \hline\hline
    RA \hfill[degree] &  \phantom{-}84.73 $\pm$  0.03 & \multirow{4}{*}{Gaia DR2}\\
    DE \hfill [degree] & -69.07 $\pm$  0.05  & \\
    $\mu_\mathrm{RA}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}1.84 $\pm$ 0.07 & \\
    $\mu_\mathrm{DE}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}0.78 $\pm$ 0.08& \\
    $\delta v_\mathrm{rad}$  \hfill[$\kms$] & \phantom{0}-45 $\pm$ 25 & \cite{bestenlehner:11}\\
    \hline
  \end{tabular}
  \label{tab:vfts682}
\end{table}
